Mice synthesizing with partitioned data

### 2020-08-08 mice_synthesizing/mice_synthesizing_partitioned_data.Rmd
Added maxit = 5

```{r}
boot_parts %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

>>>>

```{r}
boot_parts %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

Additionally, since I'm not sure whether or not it is allowed to set the number of iterations to 1, I additionally performed the same analysis with `maxit = 5`, the `mice` default for imputations.

boot_parts_5 <- boot_boys %>%
  future_map(function(x) {
    resample_partition(x, parts) %>%
      map(function(y) {
        as.data.frame(y) %>%
          mice(m = 5, 
               maxit = 5,
               method = cart,
               minbucket = 3,
               cp = 1e-08,
               predictorMatrix = pred,
               where = matrix(1, nrow(.), ncol(.)),
               print = F) %>% 
          mice::complete(., action = "long")
      }
      ) %>% bind_rows %>%
      plyr::dlply(~.imp)
  }, .options = future_options(seed = as.integer(123)), .progress = T)
```

This approach yields the following results.

```{r}
boot_parts_5 %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```
